\chapter{Structure \& Guidelines}

\section{Metadata}
\textit{Define the version, date, and unique hash of this lore iteration. This establishes the "build" of the universe.}

\section{Author Note}
\textit{A personal message from the creator. Intentions, warnings about themes, or the philosophy behind the design.}

\section{Reading Guide}
\textit{Instructions on how to navigate this document. Is it linear? Are there hidden layers? How should the fragments be pieced together?}

\section{World Rules}
\textit{The fundamental laws of physics and magic in Rusttale. Gravity, entropy, resource management, and the limitations of the engine.}

\section{Consciousness Model}
\textit{How is sentience defined? The difference between NPCs, the Player, and the Protagonist. The mechanics of the "Soul".}

\section{System Architecture}
\textit{The meta-layer. The simulation, the code, the glitches. How the technical constraints of Rust and Tetra influence the lore.}

\section{Entities}
\textit{Profiles of key characters, enemies, and anomalies. Their origins, functions, and relationships.}

\section{Player Position}
\textit{Who is the player? An observer? A god? A virus? The relationship between the input (keyboard/mouse) and the outcome.}

\section{Time Model}
\textit{Linearity vs. Loops. Save states, resets, and the persistence of memory across timelines.}

\section{Canon Events}
\textit{The fixed points in history that must happen. The immutable truths of the timeline.}

\section{Missing Events}
\textit{Corrupted data. Events that are referenced but deleted or inaccessible. The voids in history.}

\section{Narrative Fragments}
\textit{Short stories, letters, logs. Disconnected pieces of lore that build the atmosphere.}

\section{Dialogues}
\textit{Key conversations between entities. Transcripts of critical moments.}

\section{Internal Monologue}
\textit{The protagonist's inner thoughts. The struggle against the code or the player's control.}

\section{Cognitive States}
\textit{Sanity levels. The corruption of the mind. How the environment affects the psyche.}

\section{Decision Model}
\textit{Branching paths. The illusion of choice vs. actual agency. The consequences of actions.}

\section{Failure Modes}
\textit{Game over states. Glitches that halt progress. The "Blue Screen of Death" equivalents in the lore.}

\section{Unreliable Narration}
\textit{Contradictions in the story. Why the narrator might be lying or mistaken.}

\section{Open Questions}
\textit{Mysteries left intentionally unsolved. Fuel for community theories.}

\section{Ending State}
\textit{The possible conclusions. The "True Ending", "Bad Ending", and "Glitch Ending".}

\section{Glossary}
\textit{Definitions of specific terms used in the Rusttale universe.}

\section{Dev Notes}
\textit{Meta-commentary from the developers. Technical challenges that became lore features.}

\section{End of Book}
\textit{The final closing statement. A goodbye or a "See you in the next loop".}
